XX

### 2019-05-26 paper/manuscript.Rmd
Include data citations in the total citation count

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
```

@@

**Number of references:** `r n_references`

@@

```{r}
loadd(config)
loadd(int_metadata)
loadd(interaction_citations)

>>>>

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
loadd(interaction_citations)
```

@@

**Number of references:** `r n_references + nrow(interaction_citations)`

@@

```{r}
loadd(config)
loadd(int_metadata)
